Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-08 paper/sec-analysis.tex
More work on paper
more work on paper

It is also possible to define related variables like $\sqrt{d_{23}}$
that corresponds to the
splitting scale in the second-to-last clustering, though these
are mostly relevant for three-prong decays.

\item The ratio of 2-to-1-subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.

>>>>

\item The ratio of 2-to-1 subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.

### 2015-12-08 paper/sec-mva.tex
more work on paper

From the cut-based analysis,
combining the significance of the three categories,
we obtain a signal significance of $S/\sqrt{B}\simeq 1.7 (3.5)$
with all backgrounds (only QCD $4b$) taken into account.
%
This is clearly
to be enough to be able to claim observation
of Higgs pair production
in this channel, and even less to extract the trilinear Higgs  coupling
$\lambda$, in particular
taking into account the that $S/B$ is at the permille level.
%
In this section we now show how this signal significance for
 can
be significance improved when
applying a multivariate analysis (MVA) subsequently
to the cut-based analysis.

%
Multivariate techniques are by now a mature tool to enhance signal
significance in HEP analysis, allowing
to open a new window to improve the performance
of many physics analysis and searches.
%
In particular, the classification of events as arising from either signal or
background processes via the use of a multivariate analysis is a
commonly applied strategy in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.
%
For instance, the CMS $Vh(\to b\bar{b})$ analysis~\cite{Chatrchyan:2013zna}
is based on a Boosted Decision Tree (BDT) MVA, and the UCL $hh\to 4b$
feasibility study~\cite{Wardrope:2014kya}
also used  a BDT to improve signal discrimination.

In this section, first of all we present the specific MVA that we use,
based on feed-forward multi-layer neural networks.
%
We then introduce the input variables that are
used the MVA, including the jet substructure
variables, and then present the results of $S/\sqrt{B}$ including
the MVA effects.
%
Since we find that jet substructure variables are a crucial input
to the MVA, we finally show various kinematic distributions
of these variables.

@@

%
The specific type of  MVA that we use here, to
disentangle signal and background events in the $hh\to 4b$ process, will be
a multi-layer feed-forward artificial neural network (ANN),
also known as a {\it perceptron}.\footnote{This type of ANNs are the same
  as those used to parametrize Parton Distribution Functions
in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
%
This family of ANNs is sometimes known as {\it deep} neural networks, since they have
a richer architecture with hidden layers.
%
The basic idea is that the ANN is trained on an input composed on
all  signal and background
events which satisfy the requirements of the
cut-based analysis.
%
The main result of the trained ANN is identifying, in a fully automated way,
which are the most relevant variables to discriminate between the two classes
of events.

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
which is specific of the analysis category: resolved, intermediate, or boosted.
%
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the neural-network output.
%
In Fig.~\ref{fig:nnarch} we show an example of the ANN that we use in this work, corresponding here
to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).

@@

The training of the ANN for the signal/background classification task
proceeds as follows.
%
Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network parameters $\{\omega\}$, we interpret the neural network output $y_i$ (that is, the activation state of the
neuron in the last layer)
as the probability that the event $i$ originates from the signal process,
\be
y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} )\, ,
\ee
where $y_i^\prime$ represents the true classification of the event $i$, {\it i.e},
$y^\prime = 1$ for signal and $y^\prime = 0$ for background events.
%
With this interpretation, our general classification probability including background events is given by
\be
P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i} \, ,
\ee
which implies that the  negative log-likelihood error function $E(\{\omega\})$
that needs to be minimized during the ANN training is 
the cross-entropy error, defined as
 \bea
 &&E(\{\omega\}) = -\log\left(\prod_i^{N_{\text{evt}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
 &&=
 \sum_i^{N_{\text{evt}}} y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)} \, ,
 \label{cross-entropy}
 \eea
 where $N_{\text{evt}}$ is the number of
 Monte Carlo events that we have generated.
 %
 The ANN is trained both on the signal and background MC events,
 in each case using the information $y_i'$ of the true nature
 of the event.
 %
 To be stable against statistical fluctuations, it is important to use
 a large enough MC sample both of signal and of background events
 for the MVA training.

 Therefore, the training of the neural networks consist on the
 minimization of the cross-entropy error,
 Eq.~(\ref{cross-entropy}), which in this work is achieved using a
 Genetic Algorithm (GA).
 %
 The GA training is performed for a very large 
 number of generations, in this case $N_{\rm gen}=50k$, to avoid
 under-training.
 %
 We have verified that if a larger number of generations
 are used the results are unchanged.
 %

 In order to avoid over-fitting,
 we have used a cross-validation stopping
 criterion, in particular, the same one as
 that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}
 does not modify the results.
 %
 This cross-validation entails dividing the input MC dataset into two disjoint sets,
 and use one for the training and the other for the validation: the optimal
 stopping point is then indicated by the minimum of the error function
 Eq.~(\ref{cross-entropy}) for the validation sub-sample.

@@

 To identify the variables with higher discriminatory power,
 we need to train
 the MVA using a large number of kinematic distributions for
 signal and background events.
%
In this work we use different sets of
input variables for the MVA for the three categories.
%
In particular, in the case of large-$R$ jets (for the boosted
and intermediate categories) we are exploiting the jet
substructure information.

For the three categories, boosted, intermediate and resolved,
the following common variables are used as input to the MVA:
\begin{itemize}
\item The transverse momenta of the leading and subleading Higgs, $p_{T,h_1}$ and $p_{T,h_2}$.
\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$.
\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{h,1}$ and $m_{h,2}$.
\item The invariant mass of the reconstructed Higgs pair, $m_{hh}$.
\item The separation in the $\phi$--$\eta$ plane
  between the two Higgs candidates, $\Delta R_{hh}$.
  \item The separation in $\eta$  between the two Higgs candidates, $\Delta \eta_{hh}$.
\item The separation in $\phi$  between the two Higgs candidates, $\Delta \phi_{hh}$.
\end{itemize}
In addition, in the boosted category we use
  the transverse momenta of the leading, $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and
  sub-leading, $p_{T,h_{2,1}}$ and $p_{T,h_{2,1}}$, Higgs candidate subjets.
  %
  In the resolved category instead,
  the corresponding variables are
  the transverse momenta $p_{T,i}$ of the four leading 
  $b$-tagged small-$R$ jets in the event.
  %
  In the intermediate category, we use the
  transverse momenta of the subjets
  from the large-$R$ jet $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and the
 transverse momenta $p_{T,i}$ of the two leading 
  $b$-tagged small-$R$ jets.
  %
 Therefore, we have 13 variables which are common to the three categories,
 and a total of $N_{\mathrm{var}}=13,17$ and 21 variables for the
resolvedm intermediate and boosted categories.

Given that the MVA is able to identify the most discriminatory variables
and to ignore those that have smaller effects, it is advantageous to
include as many input variables as possible.
%
This is one of the main advantages of ANNs in this context: they are
inherently redundant, so
adding additional information, even if carries very little weight,
should not degrade
the classification power of the MVA, other than making the GA
minimization less efficient.

\subsection{Post-MVA signal significance}
\label{sec:signalsignificance}

In Fig.~\ref{fig:nnresponse} we show the distribution of
the ANN output at the end of the training, for the exclusive
boosted, intermediate and resolved categories.
%
The distributions are normalized so that their integral
  adds up to one.
%
The  separation between signal and background is achieved by introducing
a cut, $y_{\rm cut}$, on the ANN output, so that MC events with $y_i\ge
y_{\rm cut}$ are classified as signal events, and those with
 $y_i <
y_{\rm cut}$ as background events.
%
Therefore,
the more separated that the two distributions are, the more efficient
the MVA discrimination will be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/Boosted_disc_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/Intermediate_disc_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/Resolved_disc_noPU.pdf}
\caption{\small The distributions, at the end of the
  GA training, 
  for the signal and background MC events in the three categories:
  boosted (upper plot), intermediate (lower left plot) and
  resolved (lower right plot), as a function of the ANN output.
  %
  All distributions are normalized so that their integrals
  add up to one.
}
\label{fig:nnresponse}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA manages
to achieve a clear discrimination between signal and background, with the two distributions
nicely peaking at 1 and at 0 respectively.
%
This indicates that introducing a suitable cut
$y_{\rm cut}$
in the ANN output will substantially reduce the background,
while keeping a reasonable signal efficiency.
%
The performance of the MVA discrimination is similar though slightly worse in the intermediate
category, and it is markedly worse in the resolved category.
%
We have traced back these differences to the use of jet substructure variables
in the boosted and intermediate categories, whose use substantially
improves the
discrimination between signal and background events.

The results for the signal selection efficiency and the 
background rejection rate as a function of the cut in the ANN output
$y_{\rm cut}$
define the so-called  Receiver-Operating Characteristic (ROC)
curve.
%
It is clear that we can achieve  high signal efficiency by using
a small value of the cut in the ANN output, but this choice will be
affected from a poor background
rejection.
%
Conversely, using a higher value of the cut will increase background rejection at the
cost of dropping signal efficiency.
%
Another important requirement on the value of $y_{\rm cut}$ is that
the  number of expected  signal events (the physical
events for a given integrated
luminosity, not the MC events used for the ANN training)
after the cut is large enough.

In Fig.~\ref{fig:exampleroc} the
we show the ROC curve for the background rejection rate as a function of the signal
  selection efficiency as the cut in the ANN output is varied.
  %
  We show the results for the three exclusive categories: boosted, intermediate
  and resolved.
%
As could already be inferred from the distribution of neural
networks output in Fig.~\ref{fig:nnresponse}, we find
that the neural network MVA is reasonably efficient
in discriminating signal over background.
%
The performance is best in the case of the boosted category,
decreasing then for the intermediate and finally for the
resolved categories, consistent with the distributions in
Fig.~\ref{fig:exampleroc}.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/roc.pdf}
\caption{\small ROC curve for the background rejection rate as a function of the signal
  selection efficiency, as the cut in the ANN output is varied.
  %
  We show the results for the three exclusive categories: boosted, intermediate
  and resolved.
}
\label{fig:exampleroc}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/nev2_noPU.pdf}
\caption{\small Number of signal (dashed lines) and background (solid lines)
  events expected at the HL-LHC as a function of the cut in the ANN output,
  for the three separate categories.
}
\label{fig:nev2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

At the end of the cut-based analysis,
combining the three categories,
we obtain a signal significance of $S/\sqrt{B}\simeq 1.7 (3.5)$
with all backgrounds (only QCD $4b$) taken into account.
%
We now show how this signal significance
 can be enhanced when the cut-based analysis
 is complemented with a multivariate analysis (MVA).
%
 Multivariate techniques are by now a mature tool
 in high-energy physics data analysis, opening
 new avenues for improving the performance
of many measurements and searches at high-energy colliders.
%
In particular, the classification of events between signal and
background processes by means of MVAs is a
commonly applied strategy in LHC
applications~\cite{Baldi:2014pta,Aaltonen:2012qt,
  Wardrope:2014kya,Chatrchyan:2013zna,Dall'Osso:2015aia}.

In this section, first of all we present the specific MVA that we use,
based on feed-forward multi-layer neural networks.
%
We then introduce the input variables that are
used the MVA, including the jet substructure
variables, and then present the results of $S/\sqrt{B}$ including
the MVA effects.
%
Since we find that jet substructure variables are a crucial input
to the MVA, we show representative kinematic distributions
for these variables.
%
Finally, we assess the robustness of the MVA strategy in
high-PU environments.

@@

%
The specific type of  MVA that we use to
disentangle signal and background events is
a multi-layer feed-forward artificial neural network (ANN),
known as a {\it perceptron}.\footnote{This type of ANNs are the same
  as those used to parametrize Parton Distribution Functions
in the NNPDF global analyses~\cite{DelDebbio:2004qj,Ball:2008by,Ball:2011mu,Ball:2010de}.}
%
This family of ANNs is also known as {\it deep} neural networks, since they have
a richer architecture with hidden layers.
%
The input to the MVA are the
signal and background
events which satisfy the requirements of the
cut-based analysis.
%
The output of the trained ANNs allows the identification, in a fully automated way,
of the most relevant variables to discriminate between 
signal and background.

In this work, the ANN that we use has the following architecture.
\be
\label{eq:nn1}
N_{\mathrm{var}}\times5\times3\times1 \, ,
\ee
where $N_{\mathrm{var}}$ represents the number of input variables for the MVA,
which is different in the resolved, intermediate, and boosted categories.
%
All neural-network layers use a sigmoid activation function, allowing
for a probabilistic
interpretation of the ANN output.
%
In Fig.~\ref{fig:nnarch} we show an illustrative
example of a ANN used in this work, corresponding 
to the case of the boosted category (thus $N_{\mathrm{var}}=21$, as we explain below).

@@

The training of the ANN for the signal/background classification task
proceeds as follows.
%
Given a set of $N_{\mathrm{var}}$  kinematic variables $\{k\}_i$ associated with the event $i$, and a set of neural network weight
parameters $\{\omega\}$, we interpret the neural network output $y_i$
(the activation state of the
neuron in the last layer)
as the probability that the event $i$ originates from the signal process,
\be
y_i = P(y^\prime_i=1|\{k\}_i, \{\omega\} )\, ,
\ee
where $y_i^\prime$ represents the true classification of the event $i$, {\it i.e},
$y^\prime = 1$ for signal and $y^\prime = 0$ for background events.
%
With this interpretation, our general classification probability including background events is given by
\be
P(y_i^\prime|\{k\}_i, \{\omega\}) = y_i^{y^\prime_i}(1-y_i)^{1-y^\prime_i} \, ,
\ee
which implies that the  error function $E(\{\omega\})$
that needs to be minimized during the ANN training is 
the cross-entropy function, defined as
 \bea
 &&E(\{\omega\}) \equiv -\log\left(\prod_i^{N_{\text{ev}}} P(y_i^\prime|\{k\}_i, \{\omega\})\right)\nonumber\\
 &&=
 \sum_i^{N_{\text{ev}}} \lc y^\prime_i\log{y_i} + (1-y^\prime_i)\log{(1-y_i)}\rc \, ,
 \label{cross-entropy}
 \eea
 where $N_{\text{ev}}$ is the number of
 Monte Carlo events that are used for the ANN training.
 %
 The ANN is trained both on the signal and background MC events,
 so it is crucial to ensure that the input MC sample is large enough
 to avoid the contamination from MC statistical fluctuations.

 The training of the neural networks thus consist on the
 minimization of the cross-entropy error,
 Eq.~(\ref{cross-entropy}), which in this work is achieved using a
 Genetic Algorithm (GA).
 %
 Genetic Algorithms~\cite{quevedo,tau,Abel:2014xta,Nesseris:2012tt} are
 non-deterministic
 minimization strategies suitable for the solution
 of complex optimization problems, for instance when a very large number
 of quasi-equivalent minima are present.
 %
 GAs are inspired on natural selection processes
 that emulate biological evolution. 
 %
 In our case, the GA training is performed for a very large 
 number of generations, $N_{\rm gen}=5\cdot 10^{4}$, to avoid the risk of
 under-training.
 %
 We have verified that if a much larger number of generations
 are used, the results are unchanged.
 %

 In order to avoid over-fitting,
 we have used a cross-validation stopping
 criterion, in particular the same one as
 that used in the NNPDF3.0 analysis~\cite{Ball:2014uwa}.
 %
 This cross-validation entails dividing the input MC dataset into two disjoint sets,
 and use one for the training and the other for the validation: the optimal
 stopping point is then indicated by the minimum of the error function
 Eq.~(\ref{cross-entropy}) for the validation sub-sample.
 %
 This indicates the point where we are training on the statistical fluctuations
 of the input MC samples, rather than in the underlying (smooth) physical
 distributions.

@@

 To ensure that we include the variables with higher discriminatory power,
 we need to train
 the MVA on a large number of kinematic distributions.
%
In this work we use different sets of
input variables for the three categories.
%
In particular, in the case of large-$R$ jets (for the boosted
and intermediate categories), we are fully exploiting the jet
substructure information.

For the three categories, boosted, intermediate and resolved,
the following common variables are used as input to the MVA:
\begin{itemize}
\item The transverse momenta of the leading and subleading Higgs, $p_{T,h_1}$ and $p_{T,h_2}$.
\item The transverse momentum of the reconstructed Higgs pair, $p_{T,hh}$.
\item The invariant masses of the leading and sub-leading Higgs candidates, $m_{h,1}$ and $m_{h,2}$.
\item The invariant mass of the reconstructed Higgs pair, $m_{hh}$.
\item The separation in the $\phi$--$\eta$ plane
  between the two Higgs candidates, $\Delta R_{hh}$.
  \item The separation in $\eta$  between the two Higgs candidates, $\Delta \eta_{hh}$.
\item The separation in $\phi$  between the two Higgs candidates, $\Delta \phi_{hh}$.
\end{itemize}
In addition, in the boosted category we use
  the transverse momenta of the leading, $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and
  sub-leading, $p_{T,h_{2,1}}$ and $p_{T,h_{2,2}}$, Higgs candidate AKT03 subjets.
  %
  In the resolved category instead,
  the corresponding variables are
  the transverse momenta $p_{T,i}$ of the four leading 
  $b$-tagged small-$R$ jets in the event.
  %
  In the intermediate category, we use the
  transverse momenta of the subjets
  from the large-$R$ jet $p_{T,h_{1,1}}$ and $p_{T,h_{1,2}}$ and the
 transverse momenta $p_{T,i}$ of the two leading 
  $b$-tagged small-$R$ jets.
  %
 Therefore, we have 13 variables which are common to the three categories.

 In the boosted and intermediate categories, we also include the jet substructure
 variables introduced in Sect.~\ref{sec:analysis} for the
 large-$R$ jets: the $k_t$ splitting scales
 $\sqrt{d_{12}}$, the ratio of 2-to-1 subjettiness $\tau_{12}$,
 and the ratios of energy correlation functions $C^{(\beta)}_2$ and
 $D_2^{(\beta)}$.
 %
 Therefore, we end up with
 a total of $N_{\mathrm{var}}=13,17$ and 21 variables for the
resolved, intermediate, and boosted categories, respectively.

Given that the MVA is able to identify the most discriminatory variables
in an automated way,
and to ignore those that have little effect, it is advantageous to
include as many input variables as possible.
%
This is one of the main advantages of ANNs in this context: they are
inherently redundant, so
adding additional information, even if carries very little weight,
should not degrade
the classification power of the MVA, other than making the GA
minimization somewhat less efficient.

\subsection{MVA results}
\label{sec:signalsignificance}

We now present the results of the MVA, first without PU, and then
later including the effects of PU.
%
First of all, in Fig.~\ref{fig:nnresponse} we show the distribution of
the ANN output at the end of the GA minimization, for the exclusive
boosted, intermediate and resolved categories.
%
All distributions are normalized so that their integral
  adds up to one.
%
The  separation between signal and background is achieved by introducing
a cut, $y_{\rm cut}$, on the ANN output, so that MC events with $y_i\ge
y_{\rm cut}$ are classified as signal events, and those with
 $y_i <
y_{\rm cut}$ as background events.
%
Therefore,
the more differentiated is the distribution of the ANN output
for signal and background events, the more efficient
the MVA discrimination will be.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
\includegraphics[width=0.65\textwidth]{plots/Boosted_disc_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/Intermediate_disc_noPU.pdf}
\includegraphics[width=0.48\textwidth]{plots/Resolved_disc_noPU.pdf}
\caption{\small The distributions, at the end of the
  GA training, 
  for the signal and background MC events in the three categories:
  boosted (upper plot), intermediate (lower left plot) and
  resolved (lower right plot), as a function of the ANN output.
}
\label{fig:nnresponse}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

From Fig.~\ref{fig:nnresponse} we see that in the boosted category the MVA manages
to achieve a clear discrimination between signal and background, with the two distributions
nicely peaking at 1 and at 0 respectively.
%
This indicates that introducing a suitable cut
$y_{\rm cut}$
in the ANN output will substantially reduce the background,
while keeping a reasonable signal efficiency.
%
The performance of the MVA discrimination is similar though slightly worse in the intermediate
and resolved categories.
%
The results for the signal selection efficiency and the 
background rejection rate as a function of the cut in the ANN output
$y_{\rm cut}$
define the so-called  Receiver-Operating Characteristic (ROC)
curve, shown in Fig.~\ref{fig:exampleroc}.
%
It is clear that we can achieve  high signal efficiency by using
a small value of $y_{\rm cut}$, but this choice will be
affected from a poor background
rejection.
%
Conversely, using a higher value of the cut will increase background rejection at the
cost of dropping signal efficiency.
%
As could already be inferred from the distribution of neural
networks output in Fig.~\ref{fig:nnresponse}, we find
that our MVA is reasonably efficient
in discriminating signal over background.
%
The performance is best in the case of the boosted category,
and then slightly worse in the resolved
and intermediate categories, consistent with the distributions of
the ANN outputs from
Fig.~\ref{fig:nnresponse}.
%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
\begin{center}
  \includegraphics[width=0.49\textwidth]{plots/roc_noPU.pdf}
  \includegraphics[width=0.49\textwidth]{plots/nev2_noPU.pdf}
\caption{\small Left: ROC curve for the background rejection rate as a function of the signal
  selection efficiency, as the cut $y_{\rm cut}$
  in the ANN output is varied.
  %
  Right: Number of signal (dashed) and background (solid)
  events expected at the HL-LHC as a function of the $y_{\rm cut}$.
}
\label{fig:exampleroc}
\label{fig:nev2}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@
